Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-09 volunteer-clouds-ieee-ci-si.tex
Volviendo a cambiar GET por GEV
Anda, que ya te vale, @fergunet. Menos mal que ha sido uno solo.

As we did in the previous subsection, we have fitted also the number
of HTTP {\tt PUT}s per worker to a GET function, with the result shown %FERGU: he cambiado GEV por GET (lo de GEV era un error, no? vayamos a que sea algo nuevo que no conozco...)
in Table \ref{tab:puts:ww}. Comparing this table with what we obtained
in the previous experiment, Table \ref{tab:puts:os}, we find higher values
for the location $\mu$ and scale $\sigma$ parameters, accounting for
the higher number of contributions per volunteer that has been
previously observed; however, the shape $\xi$ parameter is
substantially similar, with a {\em bell} shape leaning towards the
origin, indicating a pattern of a few users with many contributions
and many with few contributions. If we plot the model and the data
side by side, as shown in Figure \ref{fig:gev:w2} we see that the fit
is not so tight as in the previous case, with the model overestimating
the number of individuals with a high number contributions. This is
probably due to the fact that in the previous case, the user needed to
voluntarily reload the page to contribute the most generations, with a
{\em phase change} between the people that did so and the people that
just run the experiment until completion. In this case, however, the
user just needs to let it run, without that phase change and thus a
more {\em equalitarian} distribution of contributions.

>>>>

As we did in the previous subsection, we have fitted also the number
of HTTP {\tt PUT}s per worker to a  Generalized Extreme Value (GEV) function, with the result shown %FERGU: he cambiado GEV por GET (lo de GEV era un error, no? vayamos a que sea algo nuevo que no conozco...)
%cojollos, Fergu, si no conoces no lo cambies. 
in Table \ref{tab:puts:ww}. Comparing this table with what we obtained
in the previous experiment, Table \ref{tab:puts:os}, we find higher values
for the location $\mu$ and scale $\sigma$ parameters, accounting for
the higher number of contributions per volunteer that has been
previously observed; however, the shape $\xi$ parameter is
substantially similar, with a {\em bell} shape leaning towards the
origin, indicating a pattern of a few users with many contributions
and many with few contributions. If we plot the model and the data
side by side, as shown in Figure \ref{fig:gev:w2} we see that the fit
is not so tight as in the previous case, with the model overestimating
the number of individuals with a high number contributions. This is
probably due to the fact that in the previous case, the user needed to
voluntarily reload the page to contribute the most generations, with a
{\em phase change} between the people that did so and the people that
just run the experiment until completion. In this case, however, the
user just needs to let it run, without that phase change and thus a
more {\em equalitarian} distribution of contributions.
